Incorporating individual variation in animal movement models

### 2021-03-15 distributions_paper/format_raw_dat.Rmd
save data frame after calculating net squared displacement

# I want to include family groups in that data set, just in case we want to use that later
# The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
# I've added another group for birds (29,30) which are Yasuni birds, with overlapping territories and I would assume they are a social group.
# All others are left as unknown.
aracari_df$id <- factor(aracari_df$id, levels = unique(aracari_df$id))
unique(aracari_df$id)
aracari_df %>%
  mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
                        ifelse(id == 7, "f2",
                               ifelse(id %in% c(13, 19), "f3",
                                      ifelse(id == 22, "f4",
                                             ifelse(id == 28, "f5",
                                                    ifelse(id %in% c(49,84),
                                                           "f6", 
                                                           ifelse(id %in% c(29, 30), "f7", "unknown")
                                             ))))))) -> aracari_df
```

>>>>

# I want to include family groups in that data set, just in case we want to use that later
# The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
# I've added another group for birds (29,30) which are Yasuni birds, with overlapping territories and I would assume they are a social group.
# All others are left as unknown.
aracari_df$id <- factor(aracari_df$id, levels = unique(aracari_df$id))
unique(aracari_df$id)
aracari_df %>%
  mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
                        ifelse(id == 7, "f2",
                               ifelse(id %in% c(13, 19), "f3",
                                      ifelse(id == 22, "f4",
                                             ifelse(id == 28, "f5",
                                                    ifelse(id %in% c(49,84),
                                                           "f6", 
                                                           ifelse(id %in% c(29, 30), "f7", "unknown")
                                             ))))))) -> aracari_df

saveRDS(aracari_df, "aracari_df.RDS")
```
